Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{cccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{4-6}
                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
                                    % \cline{2-2}
            \hline
            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM       & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            \hline
            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{The performance of different systems on Libri2Mix testset. For 
            speaker similarity(last column). }
            \label{main_exp}
            This table 
      \end{center}

  \end{table*}

@@

\section{Results and Discussions}

>>>>

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{cccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{4-6}
                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
                                    % \cline{2-2}
            \hline
            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM       & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            \hline
            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
            and TSELM, we compare the speaker similarity with the discretized target speech 
            (Target-discrete-WavLM) instead of the target speech due to the observation that 
            the process of discretization already losses the speaker information (0.653 for 
            Target-discrete-WavLM). We use "\_d" to denote it.  }
            \label{main_exp}
      \end{center}
  \end{table*}

@@

\section{Results and Discussions}
Table \ref{main_exp} shows the performance of different systems on the Libri2Mix test.
The model size for Target-discrete-WavLM denotes the model size of the encoder and 
decoder, which is WavLM Large and HiFi-GAN respectively. DNSMOS is calculated over the 
test sets since it is reference-free. dWER is calculated with the clean speech instead 
of the discretized speech due to our observations that this does not make much difference. 
For TSELM-L-Hybrid and TSELM, we compute the speaker similarity with the discretized
target speech (Target-discrete-WavLM).

% instead of the target speech due to the observation that the process of discretization already losses the speaker
% information (0.653 for Target-discrete-WavLM).
